Return of the Linguist:\\Toward scalable parallel corpus generation for machine translation

### 2016-07-03 doc/paper.tex
small changes/comments

@@

\pagebreak
Now we discuss Table~\ref{tab:multeval_tst2010-fixed}.
This time there is a statistically significant improvement in TER for train2015, but not for BLEU.
Post-editing train2015 again leads to further improvement.
More surprisingly, post-edited dev2010 gets slightly better BLEU at the expense of much worse TER; this is more like Table~\ref{tab:tst2010} than Table~\ref{tab:multeval_tst2010}.
This is counter-intuitive, since you would think that removing sentences with duplicated segments from tst2010 would improve TER scores, not worsen them.
This emphasizes the fact that tuning set noise can affect bottom-line performance in relatively unpredictable ways.

\begin{table}[htb]
\begin{center}
%\begin{footnotesize}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\bf Metric & \bf System (all with post-edited {\small \tt tst2010}) & \bf Avg & \bf $\overline{s}_{\text{sel}}$ & \bf $s_{\text{Test}}$ & \bf $p$-value \\
\hline
\multirow{5}{*}{BLEU $\uparrow$}
& Our baseline & 11.4 & 0.3 & 0.2 & - \\
& Trained on {\small \tt train2015} & 11.4 & 0.3 & 0.2 & 0.44 \\
& Post-edited: {\small \tt train2015} & 11.6 & 0.3 & 0.2 & 0.01 \\
& Post-edited: {\small \tt dev2010} & \textbf{11.9} & 0.3 & 0.1 & 0.00 \\
%& Post-edited: {\small \tt train2015} and {\small \tt dev2010} & \textbf{12.2} & 0.3 & 0.1 & 0.00 \\
\hline
\multirow{5}{*}{TER $\downarrow$}
& Our baseline & 70.6 & 0.4 & 0.5 & - \\
& Trained on {\small \tt train2015} & 70.1 & 0.4 & 0.3 & 0.00 \\
& Post-edited: {\small \tt train2015} & \textbf{69.7} & 0.4 & 0.2 & 0.00 \\
& Post-edited: {\small \tt dev2010} & 75.1 & 0.5 & 0.3 & 0.00 \\
%& Post-edited: {\small \tt train2015} and {\small \tt dev2010} & 74.7 & 0.5 & 0.2 & 0.00 \\
\hline
\end{tabular}
%\end{footnotesize}
\end{center}

@@

>>>>

% TODO: adding (fairly arbitrary) out-of-domain corpus is really more like using a different model (or maybe bagging?)

@@

\pagebreak
Now we discuss Table~\ref{tab:multeval_tst2010-fixed}.
Baseline's TER score changes by about 10\% relative to TAble~\ref{tab:multeval_tst2010}, but BLEU doesn't change as much.
Apparently, BLEU is more robust to relatively minor changes?
This time there is a statistically significant improvement in TER for train2015, but not for BLEU.
Post-editing train2015 again leads to further improvement.
More surprisingly, post-edited dev2010 gets slightly better BLEU at the expense of much worse TER; this is more like Table~\ref{tab:tst2010} than Table~\ref{tab:multeval_tst2010}.
This is counter-intuitive, since you would think that removing sentences with duplicated segments from tst2010 would improve TER scores, not worsen them.
This emphasizes the fact that tuning set noise can affect bottom-line performance in relatively unpredictable ways.

% NOTE
% +0.3 BLEU -0.6 TER from post-editing the entire training corpus, esp the new 2015 additions (~25000 lines)
% +0.1 BLEU -0.2 TER from ``snoop-editing'' Moses output lexical items only. cheating takes you FAR...
\begin{table}[htb]
\begin{center}
%\begin{footnotesize}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\bf Metric & \bf System (all with post-edited {\small \tt tst2010}) & \bf Avg & \bf $\overline{s}_{\text{sel}}$ & \bf $s_{\text{Test}}$ & \bf $p$-value \\
\hline
\multirow{4}{*}{BLEU $\uparrow$}
& Our baseline & 11.4 & 0.3 & 0.2 & - \\
& Trained on {\small \tt train2015} & 11.4 & 0.3 & 0.2 & 0.44 \\
& Post-edited: {\small \tt train2015} & 11.6 & 0.3 & 0.2 & 0.01 \\
& Post-edited: {\small \tt dev2010} & \textbf{11.9} & 0.3 & 0.1 & 0.00 \\
%& Post-edited: {\small \tt train2015} and {\small \tt dev2010} & \textbf{12.2} & 0.3 & 0.1 & 0.00 \\
\hline
\multirow{4}{*}{TER $\downarrow$}
& Our baseline & 70.6 & 0.4 & 0.5 & - \\
& Trained on {\small \tt train2015} & 70.1 & 0.4 & 0.3 & 0.00 \\
& Post-edited: {\small \tt train2015} & \textbf{69.7} & 0.4 & 0.2 & 0.00 \\
& Post-edited: {\small \tt dev2010} & 75.1 & 0.5 & 0.3 & 0.00 \\
%& Post-edited: {\small \tt train2015} and {\small \tt dev2010} & 74.7 & 0.5 & 0.2 & 0.00 \\
\hline
\end{tabular}
%\end{footnotesize}
\end{center}

@@

% TODO: I think another thing that SHOULD be done, but isn't commonly done, is that for a given DOMAIN, characterize inter-annotator differences in terms of , what kind of BLEU/TER scores do typical human translations get?
